Graph bipartitioning and you

### 2015-12-08 evolutionaryComputation/2-practical/report.tex
removed a lot of text from the previous

\section{Methodology}

@@

\subsection{Speed up attempts}
I wanted my implementation to be fast, preferably faster than any other
implementation. I think I didn't succeed in this for the algorithm part
because I used a lot of slow mechanisms, such as functional combinators.
Although they don't increase the computational complexity,
they do certainly increase
the minimum required runtime. I'm quite sure that every combinator in sequence
is implemented as just another loop. However because I
run all experiments in parallel the total time may be faster. So in a way
I did succeed.

\subsubsection{Parallelization}
Since were doing string comparisons I had the idea of using parallelization to
speed up the algorithm by doing parallelization. This can be done very easily
in Scala with par collections (and the fact that immutability is default).

However once I implemented this, I came to the conclusion it was not faster.
The overhead for delegating and creating threads was more than the parallelization
gained.  After 10 minutes of waiting I decided to drop this idea
since without parallelization it took about 2 minutes.
The problem is that the evaluation function, even with gene length of 100, is
to cheap to make any reasonable parallelization effective.

So now all experiments are run at the same time. This probably increases the
average time of each `run' somewhat (not that much because the concurrent
collection does \href{http://docs.scala-lang.org/overviews/parallel-collections/configuration.html}{load balancing}).
It also drastically decreases the amount of time I have to wait. Which is quite
important, especially in the development phase.

The parallelization of experiments can be removed by deleting `par' on line 64
of Main.scala

\subsubsection{Evaluate each member on creation}
Initially my members just contained the string with the `genes'. This I passed
around and would evaluate when needed. However I realized that I could do this
evaluation eagerly on creation, to reduce the evaluation calls. A member has
to be evaluated anyways, so doing this on creation and just putting in the
evaluation saves some heavy evaluation operations.

\subsubsection{Only create children if the genes are new}
This optimization reduces the amount of evaluations required.  It becomes 
more effective at deeper generations, however it slows down the fastest 
GA's by a few milliseconds but the slower GA's  are quite a bit faster.

This can be done safely because strings are immutable and so are the members.
So I can reuse them whenever its needed.

I also had an idea of using hash-codes to reduce the amount of comparisons.
But it turns out that this increases the running time, so I quickly removed
this optimization again.

>>>>

\section{Methodology}
I coppied all the code from the previous practical into this new folder.
Then I went onto a delete rage. Most code was deleted except the Expirment
class, this will probably still be usefull.

I use git, so it doens't really matter to accidently delete to much. After
that I changed the data, I removed everything which was useless. Now the file
only contains the connection numbers. This makes parsing the file a lot
easier. I don't want to do advanced pattern matching when I can quickly modfy
the file with a few vim macros. (in this case I just did a `30x').

@@
